Multiple Dice Working as One: CAD Flows and Routing Architectures for Silicon Interposer FPGAs

### 2015-03-08 doc/journal/fpgapaperfinal/FPGAPaper/fpga2014paper.tex
Adding "more than moore" reference.
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4593 8e3573b8-cf2c-4f14-ef6d-137439e28b8b

Interposer-based FPGAs allow systems larger than a single die, making a "More than Moore" improvement on the size and number of logic cells possible, and with chips combined with far more connectivity and less delay than if they were in separate packages connected through a printed circuit board.

>>>>

Interposer-based FPGAs allow systems larger than a single die, making a "More than Moore" improvement \cite{arden2010morethan} on the size and number of logic cells possible, and with chips combined with far more connectivity and less delay than if they were in separate packages connected through a printed circuit board.
